### 2014-11-12 tex/intro.tex

The heap summary approach for symbolic execution is sound and complete
with respect to a GSE machine. We show the existence of a
bi-simulation relation. In other words, any property that can be
proved using GSE can also be proved using heap summaries, furthermore,
any property proved by heap summaries can also be proved by
GSE---given the same bounds on heap reference chains and loops.

@@

 Our analysis improves on existing GSE approaches by reducing
the size of the symbolic execution state space explored, thereby
improving scalability of symboic execution for heap manipulating
software. It improves on existing heap summarization techniques by
enabling analysis of arbitrary recursive data structures (no initial
heap configuration is required) while avoiding the imprecision
introduced by these techniques.

\nsr{a paragraph that provides a breif summary
  of the results.. would be nice if we have numbers for lazier and
  lazier Sharp as well.}
  A preliminary evaluation of our technique
shows that it can improve the scalability of symbolic execution
of heap manipulating programs X fold over GSE-based analyses
while maintaining precision and efficiency.

This paper makes the following contributions:
\begin{itemize}
\item{We present a novel inter-procedural analysis technique for 
symbolic execution of heap manipulating software which constructs 
a precise heap summary.}
\item{We use the JavaLite language~\cite{saints-MS} to formalize 
the algorithm for constructing and manipulating the heap summary
on-the-fly during symbolic execution.}
\item{We implement our approach in the Symbolic PathFinder tool and
empirically demonstrate that our technique improves
the scalability of symbolic execution of heap maninpulating software
over GSE, while maintaining efficiency and precision.}
\item{We prove that at any given point during symbolic execution, the symbolic 
heap represents the exact set of feasible concrete heap structures 
for the program under analysis.}
 \end{itemize}

%\nsr{needs
%  some text on the fact we use java lite to formalize the heap
%  summary, some key characteristicss of the heap such as the fact it
%  is a bipartiate graph with locations and referneces, properties of
%  the heap such as the determinism and immutability}
\nsr{Is any part of the formalism borrowed
from the dilligs? Which part are unique?}  \nsr{end on a couple
sentences about the various rules that will be talked about in the
paper}

\nsr{The reader should be convinced about our expressiveness
  claim here}

\nsr{a paragraph that provides intution on how we are a bisumulation
  with the GSE..reader should be convinced about the precision claim}

>>>>

The heap summary approach for symbolic execution is sound and complete
with respect to properties that are provable using GSE. This is
accomplished by showing the existence of a bisimulation relation. In
other words, any property that can be proved using GSE can also be
proved using heap summaries, furthermore, any property proved by heap
summaries can also be proved by GSE---given the same bounds on heap
reference chains and loops.

In a preliminary evaluation comparing the efficiacy of the heap
summary technique with respect to the other GSE approaches, we observe
a two-order of magnitude reduction in the total time taken to explore
the same state space. We implement the heap summary approach as an
extension to the Symbolic PathFinder symbolic execution engine and
analyze three Java data structure artifacts. For these examples, we
show that where other GSE approaches are unable to complete
exploration within the provided time bound, the summary heap finishes
exploration in a few seconds.

%shows that it can improve the scalability of symbolic execution of
%heap manipulating programs X fold over GSE-based analyses while
%maintaining precision and efficiency.

@@

%Our analysis improves on existing GSE approaches by reducing
%the size of the symbolic execution state space explored, thereby
%improving scalability of symboic execution for heap manipulating
%software. It improves on existing heap summarization techniques by
%enabling analysis of arbitrary recursive data structures (no initial
%heap configuration is required) while avoiding the imprecision
%introduced by these techniques.

%\nsr{a paragraph that provides a breif summary of the results.. would
%  be nice if we have numbers for lazier and lazier Sharp as well.}

\noindent{This paper makes the following contributions:}

\begin{description}

\item\textbf{-} Define a heap encoding as a bipartiate graph of
  references and sets of constraints over locations.

% to handle alias and efficient updates of constraints.

\item\textbf{-} Present an algorithm to initialize, summarize, and
  update the bipartiate graphs during symbolic execution.

\item\textbf{-} Show the existence of a bisimulation relation prove
  that the heap summary approach is sound and complete with respect to
  properties provable by GSE.

\item\textbf{-} Demonstrate the scability of the heap summary approach
  compared to GSE approaches.

\end{description}

\noindent{In this paper, we present a brief over of the a Java-like
  language and the encoding of heaps as a bipartiate graph. We use the
  Java-like language to define the formal semantics of the heap
  summary machine and then prove the existence of a bisumulation
  relation. Finally we present an evaluation of the heap summary
  approach. }

%\item{We present a novel inter-procedural analysis technique for 
%symbolic execution of heap manipulating software which constructs 
%a precise heap summary.}
%\item{We use the JavaLite language~\cite{saints-MS} to formalize 
%the algorithm for constructing and manipulating the heap summary
%on-the-fly during symbolic execution.}
%\item{We implement our approach in the Symbolic PathFinder tool and
%empirically demonstrate that our technique improves
%the scalability of symbolic execution of heap maninpulating software
%over GSE, while maintaining efficiency and precision.}
%\item{We prove that at any given point during symbolic execution, the symbolic 
%heap represents the exact set of feasible concrete heap structures 
%for the program under analysis.}
% \end{description}

%\nsr{needs
%  some text on the fact we use java lite to formalize the heap
%  summary, some key characteristicss of the heap such as the fact it
%  is a bipartiate graph with locations and referneces, properties of
%  the heap such as the determinism and immutability}

%\nsr{Is any part of the formalism borrowed
%from the dilligs? Which part are unique?}  \nsr{end on a couple
%sentences about the various rules that will be talked about in the
%paper}

%\nsr{The reader should be convinced about our expressiveness
%  claim here}

%\nsr{a paragraph that provides intution on how we are a bisumulation
%  with the GSE..reader should be convinced about the precision claim}
